Review questions list

### 2020-10-15 docs/revision/reply.tex
fixes:: reply

	\hl{We would to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }

@@

@@

	\hl{We very much appreciate the reviewer's remark on the missing the full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }

>>>>

	\hl{We would like to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }

@@

	\textcolor{red}{AZ: the second question makes no sense to me. The time to train an ANN is not something that we consider while building the ANN. Queite frankly I don't know how to reply.}

@@

	\hl{We very much appreciate the reviewer's remark on the missing full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }
